\documentclass[style=elcolors, mode=present]{powerdot}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{epsfig}
\usepackage{anyfontsize}
\usepackage{url}
\pdsetup{
 lf=Cyber Defense Overview,
 rf=The Cyber Kill Chain\cite{LMCO:KillChain}
}
\title{Cyber Kill Chain\cite{LMCO:KillChain}}
\author{Coleman Kane\\Coleman.Kane@ge.com}
\begin{document}
\maketitle

\begin{slide}{Cyber Kill Chain Intro}
 \begin{itemize}
 \item The Cyber Kill Chain is a generalized attack model which attempts to describe the sequences of accomplishments,
 or milestones, that an attack will need to proceed through in order to accomplish the intended objective
 of the perpetrator.
 \item While not intended to be a one-size-fits-all approach, the goal is to break an attack up
 into discernable stages, to better describe the observed uses of certain tools as well as illustrate the
 investment of the attacker at each phase, as well as to help define where and how actions of the attacker within
 each phase might be detectable.
 \end{itemize}
\end{slide}

\begin{slide}{Phase 1: Recon}
 There are seven phases defined by the Kill Chain, as described by Lockheed Martin. All of the definitions below are
 verbatim, or slightly edited from the content in LMCO's \textit{Intelligence-Driven Computer Network Defense}
 paper\cite{IntelCybDef:2011:LMCO}.
 \begin{description}
  \item[Reconnaissance] Research, identification and selection of targets, often represented as crawling
                        Internet websites such as conference proceedings and mailing lists for email addresses, social
                        relationships, or information on specific technologies.
 \end{description}
\end{slide}

\begin{slide}{Phase 2: Weaponization}
 \begin{description}
  \item[Weaponization] Coupling a remote access, or other, tool with an exploit into a deliverable payload,
                       typically by means of an automated tool (weaponizer). Increasingly, client application data files such
                       as Adobe Portable Document Format (PDF) or Microsoft Objectivesce documents serve as the weaponized
                       deliverable.
 \end{description}

 In this phase is where an attacker would also likely organize the rest of their toolchain, register new domain names if necessary,
 and activate attack infrastructure.
\end{slide}

\begin{slide}{Phase 3: Delivery}
 \begin{description}
  \item[Delivery] Transmission of the weapon to the targeted environment. The three most prevalent
                  delivery vectors for weaponized payloads by APT actors, as observed by the Lockheed Martin
                  Computer Incident Response Team (LM-CIRT) for the years 2004-2010, are email attachments,
                  websites, and USB removable media.
 \end{description}

 The attacker delivers the malicious payload to the target(s) at this stage. In many cases, this is also the Kill Chain
 phase where the attack first crosses into the border of the defender's network.
\end{slide}

\begin{slide}{Phase 4: Exploitation}
 \begin{description}
  \item[Exploitation] After the weapon is delivered to victim host, exploitation triggers intruders' code.
                      Most often, exploitation targets an application or operating system vulnerability, but it could also
                      more simply exploit the users themselves or leverage an operating system feature that auto-executes
                      code.
 \end{description}

 {\small This phase occurs when the attacker attempts to exploit a machine-level, network-level, or even human-level vulnerabilities in your
 environment in order to proceed to the next phase. The goal of this phase is to achieve adequate level of access in the target environment
 so as to install the backdoor.}
\end{slide}

\begin{slide}{Phase 5: Installation}
 \begin{description}
  \item[Installation] Installation of a remote access or other tool on the victim system allows the
                      adversary to maintain persistence inside the environment.
 \end{description}

 Once exploitation has succeeded, the attackers' tools have established adequate access to the system. This access usually provides the attacker
 with user-level or sometimes administrator-level access to the target environment. Using this access, the tools now must embed themselves in
 the environment. The goal is to maintain "\textbf{persistence}" such that access can be resumed even if systems or whole networks are restarted.
\end{slide}

\begin{slide}{Phase 6: Command \& Control (C2)}
 \begin{description}
  \item[Command \& Control] Typically, compromised hosts must beacon outbound to an
                            Internet controller server to establish a C2 channel. APT malware especially requires manual
                            interaction rather than conduct activity automatically. Once the C2 channel establishes, intruders
                            have "hands on the keyboard" access inside the target environment.
 \end{description}

 Once completed, this phase provides real-time access of the compromised system to the attacker, enabling them to access the contents of the system
 and even enabling them to utilize the compromised host to gain further access, through impersonation, to other resources on the network.
\end{slide}

\begin{slide}{Phase 7: Actions On Objectives}
 \begin{description}
  \item[Actions On Objectives] {\tiny Only now, after progressing through the first six phases, can intruders
                               take actions to achieve their original objectives. Typically, this objective is data exfiltration which
                               involves collecting, encrypting and extracting information from the victim environment; violations
                               of data integrity or availability are potential objectives as well. Alternatively, the intruders may
                               only desire access to the initial victim box for use as a hop point to compromise additional systems
                               and move laterally inside the network.}
 \end{description}

 {\small Finally, once real-time command-and-control is established, the intruder will then actually go after the intended purpose of their intrusion.
         In some cases, this may be simply gaining access to systems for executing later attacks. Other times, this might be intended to steal sensitive
         technical diagrams, formulas, access credentials for future intrusion attempts, or numerous other objectives}
\end{slide}

\begin{slide}{Risks \& Assessments}
 \begin{itemize}
  \item The imminent risk to the network is increased as the attacker gets into later phases of the kill chain
  \item The investment (and thus, expense) on the part of the attacker also increases the later they get into the kill chain
  \item One could say that: The value of detecting/preventing a serious attack increases the earlier you can accomplish it in the kill chain
  \item The amount of information available regarding the nature of an attack increases in later stages of the kill chain
 \end{itemize}
\end{slide}

\begin{slide}{Cyber Kill Chain Phases}
 ...continued from prior slide
 \begin{description}
  \item[Actions on Objectives]
 \end{description}
\end{slide}

\begin{slide}{References}
 \bibliographystyle{plain}
 \bibliography{cyberdef}
\end{slide}
\end{document}
